Spfy: distributed predictive genomics of E.coli with graph based result linkage

### 2017-08-17 paper-webserver.tex
ADD: second para for implementation

@@

Graph databases focus on describing the relationships between different data, and is one of the emerging \cite{de2015trends} database types used for biological data.
Spfy

>>>>

% para: semantic web in spfy
In Spfy, the entirety of SuperPhy's previous code is replaced with methods for handling semantic web technologies.
Generalized functions are used to convert the results from different analysis modules into a graph object, and that graph object is used to update the main graph database; information contained in the WGS file is also converted into a graph object and stored.
The use of semantic web technologies allows results to be linked to the genomes they were computed from, and all data points to share a common datastructure that can be queried together.

@@

Graph databases focus on describing the relationships between different data points, and is one of the emerging \cite{de2015trends} database types used for biological data.
Spfy
